---
title: "hw5"
author: "Huili Zheng"
date: "11/20/2021"
output: 
  github_document:
    pandoc_args: --webtex
---

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  message = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
theme_set(theme_gray(base_size = 10) + theme(legend.position = "bottom"))
```

## Probelm 1

```{r}
homicide_df = 
  read_csv("./homicide-data.csv", na = c("","Unknown")) %>%
  mutate(
    city_state = str_c(city, state),
    resolution = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest" ~ "unsolved",
      disposition == "Closed by arrest" ~ "solved"
    )
  ) %>%
  relocate(city_state) %>%
  filter(city != "TulsaAL")
```

Let's focus on Baltimore, MD.

```{r}
baltimore_df = 
  homicide_df %>%
  filter(city_state == "BaltimoreMD")

baltimore_summary = 
  baltimore_df %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  )

baltimore_test = 
  prop.test(x = baltimore_summary %>% pull(unsolved), n = baltimore_summary %>% pull(n))

baltimore_test %>%
  broom::tidy()
```

Let's try to iterate across cities.

First off, write a function and test some cities.

```{r}
prop_test_function = function(city_df){
  
  city_summary = 
    city_df %>%
    summarize(
      unsolved = sum(resolution == "unsolved"),
      n = n()
    )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  return(city_test)
}

prop_test_function(baltimore_df)

homicide_df %>%
  filter(city_state == "AlbuquerqueNM") %>%
  prop_test_function()
```

Iterate across all cities.

```{r}
results_df =
  homicide_df %>%
  nest(data = uid:resolution) %>%
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with(("conf")))

```

Try to make a plot showing estimates and confidence intervals.
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state, estimate)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low,  ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
homicide_df %>%
  group_by(city_state) %>%
  summarize(
    unsolved = sum(resolution == "unsolved"),
    n = n()
  ) %>%
  mutate(
    test_results = map2(unsolved,n,prop.test), 
    tidy_results = map(test_results, broom::tidy)
  ) %>%
  select(city_state, tidy_results) %>%
  unnest(tidy_results) %>%
  select(city_state, estimate, starts_with("conf"))
```


##  Problem 2

Read in and tidy the datasets:

```{r}
p2_df =
  tibble(
    file_name = list.files(path = './data', full.names = TRUE),
    data = map(file_name, ~read_csv(.)),
    group = case_when(
      file_name %>% str_detect("con") ~ "control",
      file_name %>% str_detect("exp") ~ "experiment",
    ),
    id = as.numeric(str_extract_all(file_name, "[0-9]+"))
  ) %>% 
  unnest(cols = c(data)) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "value"
  ) %>% 
  mutate(
    id = paste(group, "_", as.character(id), sep = ""),
    week = as.numeric(str_extract_all(week, "[0-9]+"))
  ) %>% 
  select(group, id, week, value)
p2_df
```

A spaghetti plot showing observations on each subject over time:

```{r}
p2_df %>% 
  ggplot(aes(x = week, y = value, group = id, color = group)) +
  geom_line() +
  labs(x = "Week", y = "Data", title = "Observations on each subject over time")
```

*Comments:* The values of the experiment group increase over time and the overall values of experiment group are larger than those of control group after 6 weeks.

## Problem3

First we read the dataset with missing values.

```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```

Then we create a function called `fill_NA`, which will take a vector as an argument, detect the input variable type and then fill missing values with the rules defined in the question.

```{r}
fill_na = function(x){
  
  if (class(x) == "numeric") {
    return(replace_na(x, mean(x, na.rm = TRUE)))
  } else if (class(x) == "character") {
    return(replace_na(x, "virginica")) 
  }
}
```


Lastly, apply this function to the columns of dataset using a map statement.

```{r}
output = map_df(iris_with_missing, fill_na)
output
```
